Conditional selectivity for Hexastores

### 2011-07-20 conditional/trunk/selectivity-hexastore.tex
almost eradicate "node"
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@18 43ef1190-90fd-4dd7-a769-d0121f02b80e

Previous authors have taken selectivity as analogous to the
probability of matching a SPARQL term (RDF Term or variable) with an
RDF term in the data or a SPARQL triple pattern with a triple in the
data.  For a triple, $<S, P, O>$ the selectivity is the intersection
of the selectivity of each node.

@@

Analogously\todo{anybody good at arguing this mathematically?}, the conditional selectivity for a triple $T$ can be written as 
\begin{equation}
sel(T) = sel(S \cap P \cap O) = sel(O | S \cap P) \cdot sel(P | S)
\cdot sel(S) . 
\end{equation}
We note that intersection is commutative, thus similar
relations can be shown for each permutation of nodes.

Finally, note that for unbound nodes (variables), the selectivity will
always be unity, whether conditional or independent, since it will
match all possible RDF terms.

>>>>

Previous authors have taken selectivity as analogous to the
probability of matching a SPARQL term (RDF Term or variable) with an
RDF term in the data or a SPARQL triple pattern with a triple in the
data.  For a triple, $<S, P, O>$ the selectivity is the intersection
of the selectivity of each term.

@@

Analogously\todo{anybody good at arguing this mathematically?}, the conditional selectivity for a triple $T$ can be written as 
\begin{equation}
sel(T) = sel(S \cap P \cap O) = sel(O | S \cap P) \cdot sel(P | S)
\cdot sel(S) . 
\end{equation}
We note that intersection is commutative, thus similar
relations can be shown for each permutation of terms.

Finally, note that for variables, the selectivity will always be
unity, whether conditional or independent, since it will match all
possible RDF terms.
